Analysing the effect of land-use type on the proportion of scouts

### 2021-11-09 analysis/fit_models.Rmd
added presenation for eeb and worked on manuscript as markdown document exported to word

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "DejaVuSerif", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("fit_data.R")

@@

```{r, BEL, include=FALSE, message = FALSE, warning = FALSE}

@@

all_sites[[target_site]]

@@

```{r, BFI, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, BLO, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, BUR, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, CAD, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, GIL, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, HER, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, HHS, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, HOR, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, MAK, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, MEL, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, MPA, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, ROT, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, SAU, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, SOM, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, SRA, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, STU, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, SWP, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, YAL, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, ZSL, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, make-plots, include=FALSE, message = FALSE, warning = FALSE}

@@

```{r, map-plots, include=FALSE, message = FALSE, warning = FALSE}

@@

inset <- ggplot() +
  geom_sf(
    data = worldmap,
    fill = "grey90",
    color = "#4b4949d0"
  ) +
  geom_sf(
    data = london,
    fill = "#ced0cffc",
    lwd = 0
  ) +
  coord_sf(
    xlim = c(points_area[[1]] - 0.1, points_area[[3]] + 0.1),
    ylim = c(points_area[[2]] - 0.1, points_area[[4]] + 0.1)
  ) +
  geom_point(
    data = map_data,
    aes(x = lon, y = lat, shape = model, colour = col), size = 1.5
  ) +
  geom_text(
    data = selected_sites, aes(x = lon, y = lat, label = label),
    nudge_x = c(0, -0.07), nudge_y = c(0.05, 0.05)
  ) +
  annotation_north_arrow(
    location = "tr", which_north = "true",
    style = north_arrow_fancy_orienteering,
    height = unit(10, "mm"),
    width = unit(10, "mm")
  ) +
  annotation_scale(location = "br") +
  scale_shape_manual(values = c(1, 2)) +
  scale_colour_manual(values = c("black", "red")) +
  theme_nothing() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL, y = NULL) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = .5),
    text = element_text(size = 82)
  )

@@

sites_model_plot <- plot_grid(
  merge_plot_2, aic_plot, all_sites$STU$fit, all_sites$ZSL$fit,
  labels = c("A", "B", "C", "D")
)

ggsave(
  plot = sites_model_plot,
  filename = "results/figures/sites_model_plot.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)
```

```{r, other-map-plots, include=FALSE, message = FALSE, warning = FALSE}
# other map plots
inset <- ggplot() +
  geom_sf(
    data = worldmap,
    fill = "grey90",
    color = "#4b4949d0"
  ) +
  geom_sf(
    data = london,
    fill = "#ced0cffc",
    lwd = 0
  ) +
  coord_sf(
    xlim = c(points_area[[1]] - 0.1, points_area[[3]] + 0.1),
    ylim = c(points_area[[2]] - 0.1, points_area[[4]] + 0.1)
  ) +
  geom_point(
    data = map_data,
    aes(x = lon, y = lat, shape = model, colour = model), size = 1.5
  ) +
  annotation_north_arrow(
    location = "tr", which_north = "true",
    style = north_arrow_fancy_orienteering,
    height = unit(10, "mm"),
    width = unit(10, "mm")
  ) +
  annotation_scale(
    location = "br",
    text_cex = 3
  ) +
  scale_shape_manual(values = c(1, 2)) +
  scale_colour_manual(values = c("black", "red")) +
  theme_nothing() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL, y = NULL) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = .5),
    text = element_text(size = 42)
  )

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "DejaVuSerif", size = 48)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("fit_data.R")
library(kableExtra)

@@

```{r, BEL, message = FALSE, warning = FALSE}

@@

all_sites[[target_site]]$fit_result %>%
  kbl() %>%
  kable_classic(full_width = F)

@@

```{r, BFI, message = FALSE, warning = FALSE}

@@

```{r, BLO, message = FALSE, warning = FALSE}

@@

```{r, BUR, message = FALSE, warning = FALSE}

@@

```{r, CAD, message = FALSE, warning = FALSE}

@@

```{r, GIL, message = FALSE, warning = FALSE}

@@

```{r, HER, message = FALSE, warning = FALSE}

@@

```{r, HHS, message = FALSE, warning = FALSE}

@@

```{r, HOR, message = FALSE, warning = FALSE}

@@

```{r, MAK, message = FALSE, warning = FALSE}

@@

```{r, MEL, message = FALSE, warning = FALSE}

@@

```{r, MPA, message = FALSE, warning = FALSE}

@@

```{r, ROT, message = FALSE, warning = FALSE}

@@

```{r, SAU, message = FALSE, warning = FALSE}

@@

```{r, SOM, message = FALSE, warning = FALSE}

@@

```{r, SRA, message = FALSE, warning = FALSE}

@@

```{r, STU, message = FALSE, warning = FALSE}

@@

```{r, SWP, message = FALSE, warning = FALSE}

@@

```{r, YAL, message = FALSE, warning = FALSE}

@@

```{r, ZSL, message = FALSE, warning = FALSE}

@@

```{r, make-plots, message = FALSE, warning = FALSE}

@@

```{r, map-plots, message = FALSE, warning = FALSE}

@@

inset <- ggplot() +
  geom_sf(
    data = worldmap,
    fill = "grey90",
    color = "#4b4949d0"
  ) +
  geom_sf(
    data = london,
    fill = "#ced0cffc",
    lwd = 0
  ) +
  coord_sf(
    xlim = c(points_area[[1]] - 0.1, points_area[[3]] + 0.1),
    ylim = c(points_area[[2]] - 0.1, points_area[[4]] + 0.1)
  ) +
  geom_point(
    data = map_data,
    aes(x = lon, y = lat, shape = model, colour = model), size = 1.5
  ) +
  geom_text(
    data = selected_sites, aes(x = lon, y = lat, label = label),
    nudge_x = c(0, -0.07), nudge_y = c(0.05, 0.05), size = 8
  ) +
  annotation_north_arrow(
    location = "tr", which_north = "true",
    style = north_arrow_fancy_orienteering,
    height = unit(15, "mm"),
    width = unit(15, "mm"),
    text_cex = 1.5
  ) +
  annotation_scale(
    location = "br",
    text_cex = 1.5
  ) +
  scale_shape_manual(values = c(1, 2)) +
  scale_colour_manual(values = c("black", "red")) +
  theme_nothing() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL, y = NULL) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = .5)
  )

@@

sites_model_plot <- plot_grid(
  merge_plot_2, ks_plot_dist, all_sites$STU$fit, all_sites$ZSL$fit,
  labels = c("A", "B", "C", "D"), label_size = 24
)

ggsave(
  plot = sites_model_plot,
  filename = "results/figures/sites_model_plot.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

model_sites_fits <- plot_grid(
  merge_plot_2, ks_plot_dist,
  labels = c("A", "B"), label_size = 24
)

ggsave(
  plot = model_sites_fits,
  filename = "results/figures/model_sites_fits.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

stu_zsl_fit <- plot_grid(
  all_sites$STU$fit, all_sites$ZSL$fit,
  labels = c("A", "B"), label_size = 24
)

ggsave(
  plot = stu_zsl_fit,
  filename = "results/figures/stu_zsl_fit.svg",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 100
)

```

```{r, eval = FALSE, other-map-plots, message = FALSE, warning = FALSE}
# other map plots
inset <- ggplot() +
  geom_sf(
    data = worldmap,
    fill = "grey90",
    color = "#4b4949d0"
  ) +
  geom_sf(
    data = london,
    fill = "#ced0cffc",
    lwd = 0
  ) +
  coord_sf(
    xlim = c(points_area[[1]] - 0.1, points_area[[3]] + 0.1),
    ylim = c(points_area[[2]] - 0.1, points_area[[4]] + 0.1)
  ) +
  geom_point(
    data = map_data,
    aes(x = lon, y = lat, shape = model, colour = model), size = 1.5
  ) +
  annotation_north_arrow(
    location = "tr", which_north = "true",
    style = north_arrow_fancy_orienteering,
    height = unit(10, "mm"),
    width = unit(10, "mm")
  ) +
  annotation_scale(
    location = "br",
    text_cex = 3
  ) +
  scale_shape_manual(values = c(1, 2)) +
  scale_colour_manual(values = c("black", "red")) +
  theme_nothing() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL, y = NULL) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = .5),
    text = element_text(size = 42)
  )

### 2021-11-09 analysis/landuse_effect_prop_scouts.Rmd
finished dependecy install script and updated notebook with space for a mansucript figures section
added presenation for eeb and worked on manuscript as markdown document exported to word

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(size = 18)
    )
)

library(tidyr)
library(dplyr)
library(ggfortify)
library(betareg)
library(plsRbeta)
library(lmtest)
```

@@

# check the land-use type values sum to 100%
testthat::test_that(
  "land-use type values sum to 100",
  {
    expected <- rep(100, 10)
    ans <- rowSums(urban_lu[, 3:ncol(urban_lu)])
    testthat::expect_identical(expected, ans)
  }
)
```

@@

```{r, urban_pls_loadings, message = FALSE, warning = FALSE}
print(model$pp[, 1:3])
sqrt(1 / (ncol(urban.pcadata) - 1))

@@

newdat <- data_frame(
  Comp_.1 = seq(-50, 140, 0.1),
)

@@

@@

ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlim(min(-2.5), max(3.5))
```

@@

```{r, rural_pls_loadings, message = FALSE, warning = FALSE}
model$pp[, 1:3]
sqrt(1 / (ncol(rural.pcadata) - 1))
```

@@

newdat <- data_frame(
  Comp_.1 = seq(-50, 140, 0.1),
)

@@

ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlim(min(-2.5), max(3.))
```

@@

# Combining the data

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(size = 42)
    )
)

library(cowplot)
library(tidyr)
library(dplyr)
library(ggfortify)
library(betareg)
library(plsRbeta)
library(lmtest)
library(kableExtra)
library(effects)
```

@@

# check the land-use type values sum to 100%
# testthat::test_that(
#   "land-use type values sum to 100",
#   {
#     expected <- rep(100, 10)
#     ans <- rowSums(urban_lu[, 3:ncol(urban_lu)])
#     testthat::expect_identical(expected, ans)
#   }
# )
```

@@

```{r, urban_pls_loadings, message = FALSE, warning = FALSE}
urban_loadings <- list(
  loadings = model$pp[, 1],
  cutoff = sqrt(1 / (ncol(urban.pcadata) - 1))
)

print(model$pp[, 1:3])
sqrt(1 / (ncol(urban.pcadata) - 1))

@@

newdat <- data_frame(
  Comp_.1 = seq(
    min(plsdata$Comp_.1),
    max(plsdata$Comp_.1),
    length.out = length(plsdata$Comp_.1)
  )
)

@@

# get effects
urban_fitdata <- as.data.frame(predictorEffects(plsbetamodel))$Comp_.1

@@

ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = urban_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = urban_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  )

urban.pls <- ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlab("PC 1") +
  xlim(min(-2.5), max(3.5))
urban.pls

urban_plotdata <- plotdata[, 1:2]
urban_plotdata$`Land-use` <- "Urban"

@@

```{r, rural_pls_loadings, message = FALSE, warning = FALSE}
agrirural_loadings <- list(
  loadings = model$pp[, 1],
  cutoff = sqrt(1 / (ncol(rural.pcadata) - 1))
)
save(agrirural_loadings, urban_loadings, file = "results/pls-loadings.RData")

model$pp[, 1:3]
sqrt(1 / (ncol(rural.pcadata) - 1))
```

@@

newdat <- data_frame(
  Comp_.1 = seq(
    min(plsdata$Comp_.1),
    max(plsdata$Comp_.1),
    length.out = length(plsdata$Comp_.1)
  )
)

newdat$fit <- predict(plsbetamodel, newdat, se.fit = TRUE, type = "response")

rural_fitdata <- as.data.frame(predictorEffects(plsbetamodel))$Comp_.1

@@

ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = rural_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = rural_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  )

agri.rural.pls <- ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlab("PC 1") +
  xlim(min(-2.5), max(3.))
agri.rural.pls
agrirural_plotdata <- plotdata[, 1:2]
agrirural_plotdata$`Land-use` <- "Agri-rural"

@@

# Figures, results write up and main discussion points for manuscript

input figure stuff here.

```{r, manuscript-figures, message = FALSE, warning = FALSE}

plotdata <- rbind(urban_plotdata, agrirural_plotdata)
urban_fitdata$`Land-use` <- "Urban"
rural_fitdata$`Land-use` <- "Agri-rural"
fit_data <- rbind(urban_fitdata, rural_fitdata)

landuse_plots <- ggplot(data = plotdata, aes(x = Comp_.1, y = prop.scouts)) +
  geom_point() +
  geom_line(data = fit_data, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = fit_data,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  xlab("PC 1") +
  ylab("Estimated proportion of scouts") +
  facet_wrap(~`Land-use`, nrow = 1, scales = "free_x")

ggsave(
  plot = landuse_plots,
  filename = "results/figures/landuse_plots.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

landuse_plots
```

```{r, presentation.figures, message = FALSE, warning = FALSE}
urban_fit <- ggplot(data = urban_plotdata, aes(x = Comp_.1, y = prop.scouts)) +
  geom_point() +
  geom_line(data = urban_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = urban_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  xlab("PC 1") +
  ylab("Estimated proportion of scouts")

agri_rural_fit <- ggplot(data = agrirural_plotdata, aes(x = Comp_.1, y = prop.scouts)) +
  geom_point() +
  geom_line(data = rural_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = rural_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  xlab("PC 1") +
  ylab("Estimated proportion of scouts")

ggsave(
  plot = urban_fit,
  filename = "results/figures/urban_fit.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

ggsave(
  plot = agri_rural_fit,
  filename = "results/figures/agrirural_fit.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

```{r}

argi.rural.loadings <- tibble(
  "Land-use" = names(agrirural_loadings$loadings),
  "Correlation" = agrirural_loadings$loadings
)

urban.loadings <- tibble(
  "Land-use" = names(urban_loadings$loadings),
  "Correlation" = urban_loadings$loadings
)

argi.rural.loadings %>%
  mutate(Correlation = round(Correlation, 3)) %>%
  mutate(
    Correlation = cell_spec(
      Correlation,
      bold = ifelse(
        Correlation > agrirural_loadings$cutoff,
        TRUE,
        ifelse(
          Correlation < -agrirural_loadings$cutoff,
          TRUE,
          FALSE
        )
      )
    )
  ) %>%
  kbl(
    caption = "Land-use type loadings for the first principle component on the Agri-rural sites",
    escape = F
  ) %>%
  kable_classic(full_width = F)

urban.loadings %>%
  mutate(Correlation = round(Correlation, 3)) %>%
   mutate(
    Correlation = cell_spec(
      Correlation,
      bold = ifelse(
        Correlation > agrirural_loadings$cutoff,
        TRUE,
        ifelse(
          Correlation < -agrirural_loadings$cutoff,
          TRUE,
          FALSE
        )
      )
    )
  ) %>%
  kbl(
    caption = "Land-use type loadings for the first principle component on the Urban sites",
    escape = F
  ) %>%
  kable_classic(full_width = F)
```

# Combining the data (Grant stuff)
